---
title: "PSTAT 126 HW6"
author: Mujie Wang
date: 06/08/2018
output: pdf_document
---
Problem 1
```{r}
data(state)
state.x77 = as.data.frame(state.x77)
dim(state.x77)
colnames(state.x77)[4] = 'Life.Exp'
```
(a)
```{r}
mod0 = lm(Life.Exp ~1, data = state.x77)
mod1 = lm(Life.Exp ~., data = state.x77)
step(mod0, scope = list(upper = mod1))
```
According to AIC, the "best" model has the four predictors: Murder, HS Grad, Frost and Population.

(b)
```{r}
library(leaps)
mod = regsubsets(state.x77[,-4], state.x77[,4])
sum.mod = summary(mod)
sum.mod$which

sum.mod$cp

cp = sum.mod$cp
plot(2:8, cp)
abline(1,1)
```
The Cp criterion suggests the ???best??? model with four predictors: Murder, HS Grad, Frost and Population. Cp is close to p when p=4, and the model with p = 4 is simpler than the model with p = 5 or p = 6.
(c)
```{r}
sum.mod$adjr2
plot(sum.mod$adjr2)
```
The adjusted R2 criterion suggests the ???best??? model with four predictors: Murder, HS Grad, Frost and Population. This model has the largest adjusted R2 value.


(d)
```{r}
mod.adjr2 = lm(Life.Exp ~ Population + Murder + `HS Grad` + Frost, data = state.x77) 
hv = hatvalues(mod.adjr2)
p=5
n = nrow(state.x77)
which(hv > 3*p/n)

rs = rstudent(mod.adjr2)
which(abs(rs) == max(abs(rs)))

dfs = dffits(mod.adjr2)
which(abs(dfs) == max(abs(dfs)))
```
California has the largest leverage value. Hawaii has the largest externally studentized residual and DIFFITS absolue value.

```{r}
mod.delete = lm(Life.Exp ~ Population + Murder + `HS Grad` + Frost, data = state.x77[-11,])
summary(mod.delete)
```
Problem 2
```{r}
library(MASS)
library(alr4)
data(lathe1)
```
(a)
```{r}
boxcox(Life ~ Speed + Feed + I(Speed^2) +I(Feed^2) + Speed*Feed, data = lathe1)
```
lamda = 0 is in the 95% con dence interval for lamda, and when lamda = 0, the plot suggests log-transforming the response.

(b)
```{r}
mod.reduced = lm(log(Life)~1, data = lathe1)
mod.full = lm(log(Life)~ Speed + Feed + I(Speed^2) + I(Feed^2) + Speed * Feed, data = lathe1)
anova(mod.reduced, mod.full)
```

(c)
The Null hypothesis means the response Life is not linearly related to Speed.

(d)
```{r}
mod.reduced2 = lm(log(Life)~Feed + I(Feed^2), data = lathe1)
anova(mod.reduced2, mod.full)
```
Since the p-value is very close to 0, the we reject Ho.

(e)
```{r}
fit1 = lm(log(Life) ~ Speed + Feed + I(Speed^2) +I(Feed^2) + Speed*Feed, data = lathe1) 
plot(fit1, which = 4)
abline(h = 0.5, lty = 2)

cds = cooks.distance(fit1) 
sort(cds, decreasing = TRUE)
```
The 9 and 10 cases have the largest Cook???s distance Di. Di for both cases are larger than 0.5, which suggests that the two cases might be in uential.
```{r}
fit2 = lm(log(Life) ~ Speed + Feed + I(Speed^2) +I(Feed^2) + Speed*Feed, data = lathe1[-c(9,10),])
summary(fit1)

summary(fit2)
```

The coeffcient most a ected is the main effect for Speed, while the others stay mostly the same. Also, the standard errors are uniformly smaller using the reduced data set. The R^2 and adjusted R^2 are larger using the reduced data set.